Highlighting Disputed Claims on the Web

### 2010-02-23 papers/www_disputefinder/disputefinder_final.tex
Fixed widow, as requested by printing people

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/popup_vaccine_shadow_big.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown. We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.

@@

Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them (e.g. health) or that they were expected to be knowledgeable about (e.g. something relating to their work), but were less interested in applying it to pages about topics that they were less interested in. For topics that did not affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''. Users said they read about some topics (e.g. celebrity gossip) ``for entertainment'' or ``to relax'' and so they were less interested in making sure they properly understood those topics.

>>>>

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/popup_vaccine_shadow_big2.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

\looseness -1
While Dispute Finder would likely improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown. We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.

@@

\looseness -1
Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them (e.g. health) or that they were expected to be knowledgeable about (e.g. something relating to their work), but were less interested in applying it to pages about topics that they were less interested in. For topics that did not affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''. Users said they read about some topics (e.g. celebrity gossip) ``for entertainment'' or ``to relax'' and so they were less interested in making sure they properly understood those topics.
